---
title       : Alcohol consumption application
subtitle    : Pitch Presentation - Developing Data Products
author      : Sylweser Fronczak
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : prettify      # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---


## What's the app about...

<br>
<br>
<br>
It's an R Shiny application showing alcohol consumption across some OECD countries.
<br>
(Honestly, I wanted to make an app on whisky consumption, but the complete data was hard to find).

<br>
The data used in this app comes from OECD website: http://stats.oecd.org/

--- .class #id

## What's happening there...

After user chooses two countries a plot is shown on the right side panel:

```{r, echo = FALSE, }
data <- read.csv("./data/alcohol_consumption.csv", sep=";")
year <- 1960:2013

plot(year, data[,2], 
           type="s", xlab = "Year", ylab = "Alcohol consumption (liters per capita)", 
           col="blue", lwd = 3, ylim = c(1,21), 
           main = paste("Alcohol consumption in Austria and Finland"))

lines(year, data[,9], col="red", lwd = 2)

```


--- .class #id

## What's happening there... (cont'd)

Below the plot a summary data is printed:


```{r, echo = FALSE, }
"Austria"
summary(data[, 2])    

"Finland"
summary(data[, 9])   

```

--- .class #id

## A list of countries in the dataset

```{r, echo = FALSE}
data <- read.csv("./data/alcohol_consumption.csv", sep=";")

names(data)

```
